Sequential rank agreement methods for comparison of lists

### 2015-08-06 latex/paper.Rnw
Final draft

>>>>

Another caveat with the way the sequential rank agreement is defined
is the use of the standard deviation to measure agreement. The
standard deviation is an integral part of the limits-of-agreement as
discussed by \citet{alt:bland:1983}. However, the standard deviation
can also be unstable when the number of observations is low and
alternative measures such as the mean absolute deviance may prove more
stable in some situations. However, the current definition using the
standard deviation is analogous to the approach used for agreement in
method comparisong studies.
